Automatically Splitting a Staged Lambda Calculus

### 2015-07-08 paper/paper.tex
minor
uncomment splitting section
adding appendix, and moving map there
...
algoexamples renamed examples
minor fixes
I can't remember what this change was. It's late.
supplimentified
updated format stuff

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{mathpartir}
\usepackage{bbm}
\usepackage{mathabx}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{url}
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false,unicode=true]{hyperref}
\usepackage[usenames,dvipsnames]{color}
\usepackage{cprotect}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\PrerenderUnicode{λ}
\usepackage{verbatim}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

@@

%% Vote on your favorite title! Lower is better!
\title{Data Specialization for a Staged Lambda Calculus}
\title{Algorithmically Staged Lambda Calculus}
\title{Algorithmic Staging}
\title{Automatically Splitting a Staged Lambda Calculus}

\authorinfo{Nicolas Feltman \and Carlo Angiuli \and Umut Acar \and Kayvon Fatahalian}
           {Carnegie Mellon University}
           {\{nfeltman,cangiuli,umut,kayvonf\}@cs.cmu.edu}

@@

\category{CR-number}{subcategory}{third-level}

@@

\input{example}

@@

\input{algoexamples}
\input{relatedwork}
%\input{umut}

%\appendix
%\section{Appendix Title}
%This is the text of the appendix, if you need one.

@@

% We recommend abbrvnat bibliography style.

@@

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{mathpartir}
\usepackage{bbm}
\usepackage{mathabx}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{url}
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false,unicode=true]{hyperref}
\usepackage[usenames,dvipsnames]{color}
\usepackage{cprotect}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\PrerenderUnicode{λ}
\usepackage{verbatim}
\usepackage{xspace}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem*{theorem*}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

@@

\title{Automatically Splitting a Staged Lambda Calculus}
\subtitle{(Supplementary Material in Appendix)}

\authorinfo{Anon A. Anon}%Nicolas Feltman \and Carlo Angiuli \and Umut A. Acar \and Kayvon Fatahalian}
           {Anonymous Institute}%Carnegie Mellon University}
           {anon@anon.com}%\{nfeltman,cangiuli,umut,kayvonf\}@cs.cmu.edu}

@@

%\category{CR-number}{subcategory}{third-level}

@@

\input{overview}

@@

\input{examples}
\input{relatedwork}
\input{conclusion}

%\input{umut}

@@

@@

\newpage\appendix
\input{appendix}
